Distributed Environment for Auctioning Virtual Power System Resources

### 2022-02-04 other/paper-aicts-chekan.tex
The final update, hopefully

\paragraph{Distributed scenario}
\label{sec:eval-distr}
The final “Intelligent Energy Systems” profile of the NTO in 2020 was held from March 10 to 14. 60 schoolchildren from different cities of Russia, united in 13 teams, competed in a shared virtual environment while physically being in three different places:
school №709 Moscow (4 teams),
Tyumen State University (5 teams),
Novosibirsk State Technical University (4 teams).
It is worth noting that this was the first approbation of the updated auction system, and the specified configuration is the maximum on which the powerstand has ever been operated. The testing was successful. Thanks to the optimized architecture, the delays between state changes averaged no more than 1 second due to the processing of the JSON packet in the web interface. The peak delay was about 3 seconds, caused by problems with the Internet channel at the Novosibirsk site.

\paragraph{High-load local scenario}
\label{sec:eval-high}
From March 29 to April 3, 2021, Tyumen State University hosted the finals of the "Intelligent Energy Systems" profile of the NTO. 10 teams took part in this final. But due to organizational difficulties, all teams were placed on the same site. It meant the need to configure a set of stands for 10 participants. It became the primary technical challenge of the event. So, 4 stands were set up (and, accordingly, 4 servers), the game core and auction relay were placed on one of these servers, the rest of the necessary components were placed on the rest. All computers (4 servers and 10 terminals) were connected to the same physical network with a router.

@@

Being based on SSH tunnels, the architecture configuration is static at the system level, and connections are made according to the “allow list” principle, which is why any change in the architecture requires the action of developers. At the same time, authentication is currently absent, and the player is determined through the mediator configuration based on the trust of the nodes for each other. At the same time, the implementation of the authorization will be required only in scenarios for operating the module outside the current architecture and can be implemented in the future.

>>>>

\paragraph{Distributed scenario.}
\label{sec:eval-distr}
The final “Intelligent Energy Systems” profile of the NTO in 2020 was held from March 10 to 14. 60 schoolchildren from different cities of Russia, united in 13 teams, competed in a shared virtual environment while physically being in three different places:
school №709 Moscow (4 teams),
Tyumen State University (5 teams),
Novosibirsk State Technical University (4 teams).
It is worth noting that this was the first approbation of the updated auction system, and the specified configuration is the maximum on which the powerstand has ever been operated. The testing was successful. Thanks to the optimized architecture, the delays between state changes averaged no more than 1 second due to the processing of the JSON packet in the web interface. The peak delay was about 3 seconds, caused by problems with the Internet channel at the Novosibirsk site.

\paragraph{High-load local scenario.}
\label{sec:eval-high}
From March 29 to April 3, 2021, Tyumen State University hosted the finals of the ``Intelligent Energy Systems'' profile of the NTO. Ten teams took part in this final. But due to organizational difficulties, all teams were placed on the same site. It meant the need to configure a set of stands for 10 participants. It became the primary technical challenge of the event. So, 4 stands were set up (and, accordingly, 4 servers), the game core and auction relay were placed on one of these servers, the rest of the necessary components were placed on the rest. All computers (4 servers and 10 terminals) were connected to the same physical network with a router.

@@

Being based on SSH tunnels, the architecture configuration is static at the system level, and connections are made according to the “allow list” principle, that is why any change in the architecture requires the interference of developers. At the same time, authentication is currently absent, and the player is determined through the mediator configuration based on the trust of the nodes for each other. At the same time, the implementation of the authorization will be required only in scenarios for operating the module outside the current architecture and can be implemented in the future.
